Regional and Urban Economics

### 2023-02-20 Retail Agglomeration_abstract_introduction_theori_econometric_approach.qmd
wrong document

According to the Alons's model dentist should locate in the retail area for higher volume of sales.
Dentist being placed further out in to other retail agglomeration areas can also be a good strategy.
However, the dentist would then rely on the area having less competition so the rate between competition and population density are proportional.
Our findings in QGIS shows that in areas of high population density, the number of dentist also increase.
The consumer/patient then has more to choose between and the dentist also has a bigger scale of potential customers.
Where in smaller areas it is less competition and the dentist would appear to have somewhat of a monopoly since the transportation cost to the second closes dentist are noticeable higher.

Furthermore, being aware of the fact that going to the dentist is a public services and most people get assigned to their closest dentist based on their living address.
This also takes away some of the competition and would support placement in more rural areas.
More-so, is important to notice that when passed 18 years of age, you could risk loosing your local public dentist due to lack of capacity.
Suggesting some dentist might seek closer to CBD areas to capture most of the remaining part of the population.
Business, public places and industry can have a positive effect on revenue since this is areas where most of the population spends their time during their day, either going to work, school and other errand.
Reducing the transportation cost for the customer as they are already located in these areas even if they do not live here.

@@

Hva viser informasjonen om vinmonopolet?

@@

>>>>

The size of the mall also has a positive effect on revenue for dentist practice, as larger malls tends to have have positive effect on the revenue.
Larger malls gives the customer more options to choose from and are often placed closer to a larger CBD which might be more attractive for customers to visit, and then also explaining why customers could be more interested in traveling further to visit these malls instead of visiting the local mall in a smaller CBD.

More so, the reasoning for a more profitable business close to a shopping malls can be explain by customers beeing able to combine their dentis visit with shopping afterwards, maybe in a way to threat them self.
You can find some similiarities in marketing strategies for grocery stores in the sense where they alwyas have a well planned system of where all their products are.
Where for example gums and grab and go snacks, will always be placed next to the cashier.
these are usually cheap, small and quick to consume, and something that you dont usually look for, but since you are already there, you might aswell.
Same thoughts goes for people who visit the dentists in or fairly close to a mall.
they are already there and might aswell be done with their shopping.
This tradeoff can be highly beneficial for the mall itself, considering the patients going to the dentists then also become customers of the mall by default.

\
According to the Alons's model dentist should locate close to the CBD for higher volume of sales.
Dentist being placed further out in to other retail agglomeration areas can also be a good strategy.
However, the dentist would then rely on the area having less competition so the rate between competition and population density are proportional.
Our findings in QGIS shows that in areas of high population density, the number of dentist also increase.
The consumer/patient then has more to choose between and the dentist also has a bigger scale of potential customers.
Where in smaller areas it is less competition and the dentist would appear to have somewhat of a monopoly since the transportation cost to the second closes dentist are noticeable higher.

Findings suggest that locating further away from a CBD has a positive effect on the revenue for dentist and also that moving further away from the competition has a negative effect on revenue.
These findings could come across as surprising at first, but taking in ti comparison that some of the CBD´s obtained from QGIS could be categorized as relatively small, one explanation to this would possibly be that the data contains a larger number of smaller CBD´s with fewer dentist offices that also has less potential customers and a weaker income which pulls the result in one direction.
The fact that the population density (X_sum) also shows a positive effect on the revenue strengthen this theory.
Areas with a higher population density tends to increase the revenue for dentist.

\
Furthermore, being aware of the fact that going to the dentist is a public services and most people get assigned to their closest dentist based on their living address.
This also takes away some of the competition and would support placement in more rural areas.
More-so, is important to notice that when passed 18 years of age, you could risk loosing your local public dentist due to lack of capacity.
Suggesting some dentist might seek closer to CBD areas to capture most of the remaining part of the population.
Business, public places and industry can have a positive effect on revenue since this is areas where most of the population spends their time during their day, either going to work, school and other errand.
Reducing the transportation cost for the customer as they are already located in these areas even if they do not live here.

@@

Findings around Wine monopoly shows a negative effect on turnover per capita in retail.
In other words, the Wine monopoly has a bad influence for the turnover in retail.
The explanation could be as mentioned, since Wine monopoly could be categorized as an anchor store, it drag customers from malls and areas where there is no winemonoply over to the areas and malls where a wine monopoly exist, only helping out the stores surrounding.
Another reasoning could be that the winemonopoly drags attention away from the other shopping options, resulting in a negative effect for the turnover for other retailers.

is important to notice that the municipal council is more or less in charge of where Wine monopoly is allowed to operate.
There are several criterias and factors that are taken into consideration before anything gets approved to prevent areas to dry out.
[@kvikstadSeListenDisse2019]

@@

There are several critical factors that effect the income for dental practice where our result shows that the income tends to be higher located close to a mall or inside the mall itself.
A larger mall also has a positive effect of the income.
Theorys crated by Marshall, Alonso and Keynesian helps us explain some of our findings on why malls shows a pattern to be a better location for dental practice and why there are certain areas where there is a cluster of dentist.
However, it is important to notice that a high revenue does not equal good economic results as more populated and central areas tends to have higher fees for example rent.
The Wine monopoly also appears to have negative effect on turnover per capita in retail.

##
